Analyses of Promises in R

### 2018-03-23 analysis/analysis.Rmd

---
title: "Analyses of Promises in R"
author: "Aviral Goel"
output: 
  html_document:
    theme: flatly
    highlight: tango
    keep_md: true
    toc: true
    toc_float: true
    number_sections: true
params:
  analysis_output_dir: TRUE
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(methods) ## including this prevents a warning - "executing load actions ..."
library(DT)
library(tidyverse)
library(knitr)
```

```{r echo=FALSE, message=FALSE}
# https://www.rdocumentation.org/packages/knitr/versions/1.17/topics/include_graphics
show_graph <- function(analysis_name, graph_filename) {
    file.path(params$analysis_output_dir, analysis_name, "graph", graph_filename) %>%
    include_graphics()
}

@@

## Categorization

@@

1. **Foreign Promises** are created before the tracing starts. Since we don't see their creation, 
   we can't study their lifespan in terms of GC cycles. They are **excluded from the analysis**
2. **Immortal Promises** are created but not garbage collected while tracing. They are 
   **excluded from the analysis** because we can't compute their lifespan.
3. **Mortal Promises** are created and garbage collected while tracing.
   They are the only promises that are **included in the analysis**.

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "count.png")
```

**TOTAL PROMISE COUNT** = **FOREIGN PROMISE COUNT** + **IMMORTAL PROMISE COUNT** + **MORTAL PROMISE COUNT**

@@

@@

### Insights

This categorization sheds light on how many promises are excluded from the analysis.
Clearly, the number of **Immortal Promises** and **Foreign Promises** is quite low.
Any analysis done on **Mortal Promises** should be statistically relevant.

## Alive Promise Count

The following graph shows the number of mortal promises that are alive for a given number of GC cycles.

@@

@@

### Insights

We see that most promises are alive for the shortest possible duration, i.e. - one GC cycle.
The remaining promises are a fraction of the number of promises that are alive for this duration.
We also observe a decreasing trend in the number of promise that are alive for a given number of
GC cycles, as the number of GC cycles increase. This means that most promises are used immediately
and have little need of being alive for longer durations.

## Indispensable Promise Count

@@

alive %>%
full_join(indispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
full_join(dispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
datatable(rownames = FALSE)
```

>>>>

---
title: "Analyses of Promises in R"
author: "Aviral Goel"
output: 
  html_document:
    theme: flatly
    highlight: tango
    keep_md: true
    toc: true
    toc_float: true
    number_sections: true
params:
  analysis_output_dir: TRUE
---
```{r set-options, echo=FALSE, cache=FALSE}
options(width = 1200)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(methods) ## including this prevents a warning - "executing load actions ..."
library(DT)
library(tidyverse)
library(knitr)
library(png)
library(grid)
library(gridExtra)
```

```{r echo=FALSE, message=FALSE}
# https://www.rdocumentation.org/packages/knitr/versions/1.17/topics/include_graphics

get_graph <- function(analysis_name, graph_filename) {
    file.path(params$analysis_output_dir, analysis_name, "graph", graph_filename)
}

show_graph <- function(analysis_name, graph_filename) {
    get_graph(analysis_name, graph_filename) %>%
    include_graphics()
}

@@

## Promise Categories

@@

1. **Foreign Promises** are created before the tracing starts. Since we don't see their creation, 
   we can't study their lifespan in terms of GC cycles. They are **excluded from the analysis**
2. **Immortal Promises** are created but not garbage collected while tracing. They are 
   **excluded from the analysis** because we can't compute their lifespan.
3. **Mortal Promises** are created and garbage collected while tracing.
   They are the only promises that are **included in the analysis**.
   They are further classified as follows:
   i. **Forced Promises** are the mortal promises that are looked up at least once.
   ii. **Unforced Promises** are mortal promises that are never looked up.

```{r echo=FALSE, message=FALSE, fig.width=10, fig.height=4.5}
show_graph("promise-lifespan", "counts.png")
```

**TOTAL PROMISE COUNT** = **FOREIGN PROMISE COUNT** + **IMMORTAL PROMISE COUNT** + **MORTAL PROMISE COUNT** + **UNFORCED PROMISE COUNT**

### Summarized Data

@@

### Raw Data

@@

## Promise Lifespan Distribution

The following graph shows the lifespan of mortal promises in terms of GC cycles. 
The lifespan of a promise is defined as the number of GC cycles for which the 
promise is alive.

@@

### Summarized Data

@@

## Indispensable Promises

@@

alive %>%
full_join(indispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
full_join(dispensable, by = c("GC CYCLES" = "GC CYCLES")) %>%
datatable(rownames = FALSE)
```
<!--
# Promise Space Usage

This section compares the number and size of objects allocated by R.

## R Object Count

Count of R objects.

```{r echo=FALSE, message=FALSE}
show_graph("promise-memory-usage", "promise-count.png")
```

```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "object_size_summary.csv") %>%
select(-`SIZE`, -`SCRIPT`) %>%
group_by(`OBJECT TYPE`) %>%
summarize(`MEAN` = mean(`COUNT`),
          `MEDIAN` = median(`COUNT`),
          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`COUNT`), 0.25)),
          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`COUNT`), 0.75))) %>%
datatable(rownames=FALSE)
```

```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "object_size_summary.csv") %>%
select(-`SIZE`) %>%
datatable(rownames=FALSE)
```

### Outliers

#### Lower Quantile
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "lower_count_quantile.csv") %>%
datatable(rownames=FALSE)
```

#### Upper Quantile
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "lower_count_quantile.csv") %>%
datatable(rownames=FALSE)
```

## R Object Size

Size of R objects.

```{r echo=FALSE, message=FALSE}
show_graph("promise-memory-usage", "promise-size.png")
```

```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "object_size_summary.csv") %>%
select(-`COUNT`, -`SCRIPT`) %>%
group_by(`OBJECT TYPE`) %>%
summarize(`MEAN` = mean(`SIZE`),
          `MEDIAN` = median(`SIZE`),
          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`SIZE`), 0.75)),
          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`SIZE`), 0.25))) %>%
datatable(rownames=FALSE)
```

```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "object_size_summary.csv") %>%
select(-`SIZE`) %>%
datatable(rownames=FALSE)
```

### Outliers

#### Lower Quantile
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "lower_size_quantile.csv") %>%
datatable(rownames=FALSE)
```

#### Upper Quantile
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "upper_size_quantile.csv") %>%
datatable(rownames=FALSE)
```

## R Object Count

Count of R objects.

```{r echo=FALSE, message=FALSE}
show_graph("promise-memory-usage", "promise-count.png")
```

```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "object_size_summary.csv") %>%
select(-`SIZE`, -`SCRIPT`) %>%
group_by(`OBJECT TYPE`) %>%
summarize(`MEAN` = mean(`COUNT`),
          `MEDIAN` = median(`COUNT`),
          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`COUNT`), 0.25)),
          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`COUNT`), 0.75))) %>%
datatable(rownames=FALSE)
```

```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "object_size_summary.csv") %>%
select(-`SIZE`) %>%
datatable(rownames=FALSE)
```

### Outliers

#### Lower Quantile
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "lower_count_quantile.csv") %>%
datatable(rownames=FALSE)
```

#### Upper Quantile
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "lower_count_quantile.csv") %>%
datatable(rownames=FALSE)
```

# Environment Function Usage

This section discusses the usage of functions which manipulate environments.

## baseenv()

This is the environment of the base package.

```{r echo=FALSE, message=FALSE, out.width = "400px"}
show_graph("environment", "baseenv.png")
show_graph("environment", "baseenv-relative.png")
```

## emptyenv()

This is the empty environment, the topmost environment.

```{r echo=FALSE, message=FALSE, out.width = "400px"}
show_graph("environment", "emptyenv.png")
show_graph("environment", "emptyenv-relative.png")
```

## new.env(hash = TRUE, parent = parent.frame(), size = 29L)

`new.env` returns a new (empty) environment with (by default) enclosure the parent frame.

```{r echo=FALSE, message=FALSE, out.width = "400px"}
show_graph("environment", "new.env.png")
show_graph("environment", "new.env-relative.png")
```

## NewEnvironment

This is the C level function which gets called when a new environment is created.

```{r echo=FALSE, message=FALSE, out.width = "400px"}
show_graph("environment", "NewEnvironment.png")
show_graph("environment", "NewEnvironment-relative.png")
```

## environment(fun = NULL)

If fun is a function or a formula then `environment(fun)` returns the environment associated with that function or formula. If fun is NULL then the current evaluation environment is returned.

```{r echo=FALSE, message=FALSE, out.width = "400px"}
show_graph("environment", "environment.png")
show_graph("environment", "environment-relative.png")
```

## environment(fun) <- value

`environment(fun) <- value` sets the environment of the function or formula fun to the value given.

```{r echo=FALSE, message=FALSE, out.width = "400px"}
show_graph("environment", "environment<-.png")
show_graph("environment", "environment<--relative.png")
```

## parent.env

`parent.env` returns the enclosing environment of its argument.

```{r echo=FALSE, message=FALSE, out.width = "400px"}
show_graph("environment", "parent.env.png")
show_graph("environment", "parent.env-relative.png")
```

## parent.env(env) <- value

`parent.env<-` sets the enclosing environment of its first argument.
The replacement function parent.env<- is extremely dangerous as it can be used to destructively change environments in ways that violate assumptions made by the internal C code. It may be removed in the near future.

```{r echo=FALSE, message=FALSE, out.width = "400px"}
show_graph("environment", "parent.env<-.png")
show_graph("environment", "parent.env<--relative.png")
```

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

```{r echo=FALSE, message=FALSE}
get_table("environment", "environment-function-usage.csv") %>%
select(-`SCRIPT`) %>%
group_by(`FUNCTION NAME`) %>%
summarize(`MEAN` = mean(`COUNT`),
          `MEDIAN` = median(`COUNT`),
          `LOWER QUANTILE (25%)` = unname(stats::quantile(sort(`COUNT`), 0.25)),
          `UPPER QUANTILE (75%)` = unname(stats::quantile(sort(`COUNT`), 0.75))) %>%
datatable(rownames=FALSE)
```

#### Raw
```{r echo=FALSE, message=FALSE}
show_table("environment", "environment-function-usage-spread.csv")
```

### Outliers

#### Lower Quartile
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "lower_size_quantile.csv") %>%
datatable(rownames=FALSE)
```

#### Upper Quartile
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "upper_size_quantile.csv") %>%
datatable(rownames=FALSE)
```
-->

### 2018-03-23 analysis/report/01-lifespan.Rmd

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(methods) ## including this prevents a warning - "executing load actions ..."
library(DT)
library(tidyverse)
library(knitr)
library(png)
library(grid)
library(gridExtra)
```

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(methods) ## including this prevents a warning - "executing load actions ..."
library(DT)
library(tidyverse)
library(knitr)
library(png)
library(grid)
library(gridExtra)
library(broom)
library(tidyr)
```

### 2018-03-23 analysis/report/02-memory.Rmd

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("promise-memory-usage", "promise_count.png")
show_graph("promise-memory-usage", "relative_count.png")
```

### Absolute Count Quantiles 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "quantiles.csv") %>%
filter(`QUANTITY` == "COUNT") %>%
spread(QUANTILE, VALUE) %>%
select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
datatable(rownames = FALSE)
```

### Absolute Count Outliers 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "outliers.csv") %>%
filter(`QUANTITY` == "COUNT") %>%
select(`OBJECT TYPE`, `SCRIPT`, `COUNT`) %>%
datatable(rownames = FALSE)
```

### Relative Count Quantiles 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "quantiles.csv") %>%
filter(`QUANTITY` == "RELATIVE COUNT") %>%
spread(QUANTILE, VALUE) %>%
select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
datatable(rownames = FALSE)
```

### Relative Count Outliers 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "outliers.csv") %>%
filter(`QUANTITY` == "RELATIVE COUNT") %>%
select(`OBJECT TYPE`, `SCRIPT`, `RELATIVE COUNT`) %>%
datatable(rownames = FALSE)
```

@@

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("promise-memory-usage", "promise_size.png")
show_graph("promise-memory-usage", "relative_size.png")
```

### Absolute Size Quantiles 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "quantiles.csv") %>%
filter(`QUANTITY` == "SIZE") %>%
spread(QUANTILE, VALUE) %>%
select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
datatable(rownames = FALSE)
```

### Absolute Size Outliers 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "outliers.csv") %>%
filter(`QUANTITY` == "SIZE") %>%
select(`OBJECT TYPE`, `SCRIPT`, `SIZE`) %>%
datatable(rownames = FALSE)
```

### Relative Size Quantiles 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "quantiles.csv") %>%
filter(`QUANTITY` == "RELATIVE SIZE") %>%
spread(QUANTILE, VALUE) %>%
select(`OBJECT TYPE`, `0%`, `25%`, `50%`, `75%`, `100%`) %>%
datatable(rownames = FALSE)
```

### Relative Size Outliers 
```{r echo=FALSE, message=FALSE}
get_table("promise-memory-usage", "outliers.csv") %>%
filter(`QUANTITY` == "RELATIVE SIZE") %>%
select(`OBJECT TYPE`, `SCRIPT`, `RELATIVE SIZE`) %>%
datatable(rownames = FALSE)
```

## Raw Data
```{r echo=FALSE, message=FALSE}
show_table("promise-memory-usage", "object_size_summary.csv")
```

>>>>

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("promise-memory-usage", "object_count.png")
show_graph("promise-memory-usage", "relative_object_count.png")
```

@@

```{r echo=FALSE, message=FALSE, out.width="575px"}
show_graph("promise-memory-usage", "object_size.png")
show_graph("promise-memory-usage", "relative_object_size.png")
```

## Summarized Data
```{r echo=FALSE, message=FALSE}
show_table("promise-memory-usage", "summary.csv")
```

## Raw Data
```{r echo=FALSE, message=FALSE}
show_table("promise-memory-usage", "raw.csv")
```
